preprocessing

### 2022-11-14 r-prep/prep.Rmd
EU-28
renaming
data set

```{r}
data_gwp100 = read_excel("data-raw/essd_ghg_data_gwp100.xlsx",sheet = "data")
load("data-raw/data_wdi.RData") 
data_wdi %<>%
  select(-country)

data_base = data_gwp100 %>%
  left_join(data_wdi,by=c("ISO","year")) %>%
  mutate(GHG_pc = GHG/pop) %>%
  mutate(GDP_pc = gdp_ppp/pop)

>>>>

```{r}
data_gwp100 = read_excel("data-raw/egr22_country_data.xlsx",sheet = "data")
load("data-raw/data_wdi.RData") 
data_wdi %<>%
  select(-country)

data_base = data_gwp100 %>%
  rename(ISO = iso) %>%
  left_join(data_wdi,by=c("ISO","year")) %>%
  mutate(GHG_pc = GHG/pop) %>%
  mutate(GDP_pc = gdp_ppp/pop) %>%
  filter(year <= 2020) %>% 
  mutate(
    EU = case_when(country %cin% eurostat::eu_countries[2]~ TRUE),

  )
